Arc Blanc: a real time ocean simulation framework

### 2024-11-14 paper.tex
presents previous works -> presents the previous works...
Motivate using Cords

This article is organized as follows.
Section~\ref{sec:relatedwork} presents previous works related to ocean simulation, including its interaction with solid.
Sections \ref{sec:oceanWaves} to \ref{sec:solidToFluidAction} detail \framework, including the ocean surface simulation in Section~\ref{sec:oceanWaves}, the action of the fluid to solids in Section~\ref{sec:fluidToSolidAction} and the action of a solid to the fluid in Section~\ref{sec:solidToFluidAction}.
Section~\ref{sec:results_and_discussions} discusses some results obtained with \framework.
At last, Section~\ref{sec:conclusions} gives general conclusions.

@@

\subsubsection{Ocean free surface simulation}
\label{subsubsec:oceanFreeSurfaceSim}
J. Tessendorf (2004) \cite{tessendorfSimulatingOceanWater1999} presented what could be considered a seminal work in real-time ocean simulation. His work relies on the Fast Fourier Transform (FFT) and statistical wave spectra to accurately find the analytical solutions to an approximation of the Navier-Stokes equation on a 2D height field. This method is commonly known as the “Tessendorf method”.

@@

For solid-fluid coupling, \framework based its calculations on the FDM described in Gomez (2000) \cite{gomezInteractiveSimulationWater2000} and its improvement by Cords and Staadt (2009) \cite{cordsRealTimeOpenWater2009}.
%-------------------------------------------------------------------------
\section{Ocean waves}
\label{sec:oceanWaves}
This section summarizes Tessendorf's method and the various improvements it has received.
It also presents our first contributions: calculation of the fluid velocity at any depth.

>>>>

This article is organized as follows.
Section~\ref{sec:relatedwork} presents the previous works related to ocean simulation, including its interaction with solid.
Sections \ref{sec:oceanWaves} to \ref{sec:solidToFluidAction} detail \framework, including the ocean surface simulation in Section~\ref{sec:oceanWaves}, the action of the fluid to solids in Section~\ref{sec:fluidToSolidAction} and the action of a solid to the fluid in Section~\ref{sec:solidToFluidAction}.
Section~\ref{sec:results_and_discussions} discusses some results obtained with \framework.
At last, Section~\ref{sec:conclusions} gives general conclusions.

@@

\subsubsection{Ocean free surface simulation}
\label{subsubsec:oceanFreeSurfaceSim}
J. Tessendorf (2004) \cite{tessendorfSimulatingOceanWater1999} presented what could be considered a seminal work in real-time ocean simulation. His work relies on the Fast Fourier Transform (FFT) and statistical wave spectra to accurately find the analytical solution to an approximation of the Navier-Stokes equations on a 2D height field. This method is commonly known as the “Tessendorf method”.

@@

For solid-fluid coupling, \framework based its calculations on the FDM described in Gomez (2000) \cite{gomezInteractiveSimulationWater2000} and its improvement by Cords and Staadt (2009) \cite{cordsRealTimeOpenWater2009}, because its ability to be real-time while providing quite realistic behavior.

%-------------------------------------------------------------------------
\section{Ocean waves}
\label{sec:oceanWaves}
This section summarizes Tessendorf's method and the various improvements it has received.
It also presents our first contributions: calculation of the fluid velocity at any depth.
